\propertitle

### 2019-06-17 maxNt_v5.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-17T10:56:29+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The context we consider is as follows. We have recorded the spiking
activities of $n$ neurons for a given amount of time. Let's call these
neurons the \enquote{sample}. Their spikes are binned into $T$ time bins and
binarized to $\set{0,1}$ values in each bin. Denote by $\ya_{t}$ the number
of neurons that fire during time bin $t$, divided by the total number of
neurons $n$; we call this the \emph{normalized total activity} of the
sample, or just its \enquote{total activity} or \enquote{activity} for
short. Obviously $\ya_{t} \in\set{0,1/n,\dotsc,(n-1)/n,1}$; if $\ya_{t}=0$,
no neuron spiked during time bin $t$; if $\ya_{t}=1$, all spiked at some
point during time bin $t$. For brevity, let's say \enquote{at $t$} for
\enquote{during time bin $t$}.

@@

In our case, to apply the method for the total activity of the full
network we need to fix some of the latter's expectation values, for
example its moments. But we don't have any measured averages for the full
network to equate our expectations to. Here enters
point~\ref{item:sample_step}: the probability calculus gives an exact,
linear relation between the first $m$ moments for the full network and
the first $m$ for the sample; the ones determine the others and vice versa
at every time bin \citep[for example][\eqns~(16)]{portamanaetal2015}. This
relation is a classical result of sampling theory
\citep[\chaps~I--IV]{whitworth1867_r1965}[\chap~II]{feller1950_r1968}[\chap~3]{jaynes1994_r2003}[see
also][]{whitworth1897}.

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2019-06-17T11:00:59+0200
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{***}
\newcommand*{\propertitle}{Maximum-entropy distributions for a 
  neuronal network\\ from subnetwork data%\\{\large ***}%
}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Maximum-entropy from sample data}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, V. Rostami, E. Torre}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

The context we consider is as follows. We have recorded the spiking
activities of $n$ neurons for a given amount of time. Let's call these
neurons the \enquote{sample} or the \enquote{subnetwork}. Their spikes are
binned into $T$ time bins and binarized to $\set{0,1}$ values in each bin.
Denote by $\ya_{t}$ the number of neurons that fire during time bin $t$,
divided by the total number of neurons $n$; we call this the
\emph{normalized total activity} of the sample, or just its \enquote{total
  activity} or \enquote{activity} for short. Obviously
$\ya_{t} \in\set{0,1/n,\dotsc,(n-1)/n,1}$; if $\ya_{t}=0$, no neuron spiked
during time bin $t$; if $\ya_{t}=1$, all spiked at some point during time
bin $t$. For brevity, let's say \enquote{at $t$} for \enquote{during time
  bin $t$}.

@@

In our case, to apply the method for the total activity of the full network
we need to fix some of the latter's expectation values, for example its
moments. But we don't have any measured averages for the full network to
equate our expectations to. Here enters point~\ref{item:sample_step}: the
probability calculus gives an exact, linear relation between the first $m$
moments for the full network and the first $m$ for the sample
\citep[\eqns~(16)]{portamanaetal2015}; the ones determine the others and
vice versa at every time bin. This relation is a classical result of
sampling theory
\citep[\chaps~I--IV]{whitworth1867_r1965}[\chap~II]{feller1950_r1968}[\chap~3]{jaynes1994_r2003}[see
also][]{whitworth1897}.
